Supplementary Materials

### 2020-05-29 analysis/analysis.Rmd
Coloured coded table

glimpse(subgroups)
opts <- options(knitr.kable.NA = "")
knitr::kable(index_table, caption = "subgroup index")
```

```{r}
knitr::kable(normal_table, caption = "normal and non-normal subgroups")
```

>>>>

glimpse(subgroups)

opts <- options(knitr.kable.NA = "")

knitr::kable(index_table, caption = "subgroup index", escape = "F") %>% kableExtra::kable_styling(full_width = F)
```
